Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-05 manuscript-figures.Rmd
update supplementary figures

data.R0_norm <- data.R0 %>%
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>%
  filter(KH %in% newKH_vals) %>%
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>%
  # mutate(mean_norm = mean / max(mean)) %>%
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>%
  # mutate(lowHCI_norm = lowHCI / max(median)) %>%
  arrange(system_ID, sigmaH, KH, Temperature, median_norm)

@@

Toptalt_df <- data.Topt %>%
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>%
  distinct() %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, mean) %>%
  mutate(sigmaH_proxy = sigmaH)

@@

# Plot mean of Topt heat map
Toptalt_plots <- Toptalt_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # Topt for FINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy < 10^2.2),
    breaks = Topt_breaks
  ) +
  # Topt for INFINITE sigmaH:
  # take mean of mean to hide variation from artifacts of uncertainty
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy > infinite_skew) %>%
      group_by(system_ID) %>%
      mutate(mean = mean(mean), .groups = "keep"),
    size = 1,
    breaks = Topt_breaks
  ) +
  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
  geom_contour(
    data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
    aes(y = sigmaH, z = mean, colour = "R0 = 1"),
    breaks = min(filter(data.CT, variable == "CTwidth", mean > 0)$mean),
    size = 1
  ) +
  # geom_contour(data = data.R0_norm,
  #              aes(y = sigmaH, z = mean, colour = "R0=1"), breaks = c(1), size = 1) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

@@

CTwidth_df <- data.CT %>%
  ungroup() %>%
  mutate(system_label = case_when(
    system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
    system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
    system_ID == "Aedes albopictus / DENV" ~ "(c\u200b) *Ae. albopictus* and DENV",
    system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
    system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
  )) %>%
  filter(variable == "CTwidth") %>%
  # filter(sigmaH < 10^2.2) %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>%
  ungroup()

@@

CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal mean_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = mean)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < 10^2.2)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(
    CTwidth_df,
    sigmaH_proxy > 10^2.4,
    sigmaH_proxy < infinite_divide
  )) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Parasite thermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

<!-- # Supplementary Figures -->

<!-- ```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'} -->
<!-- # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density. -->

<!-- # x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity") -->
<!-- # y = Temperature -->
<!-- # color = R0 -->
<!-- # curves: -->
<!-- #   R0 = 1 contour (black curve) -->
<!-- #   Topt (red curve) -->

<!-- # Facets: -->
<!-- # Rows = levels of vertebrate host population density -->
<!-- # Columns = two MBPT systems -->
<!-- # Total = 6 plots -->

<!-- ## Set up plot data frame -->
<!-- # We re-create the output data frame so that we can vary sigmaH correctly. -->
<!-- # We also drop the resolution of KH down to just three values -->
<!-- # Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald" -->

<!-- ## Configure data frame for plotting -->
<!-- R0_df <- data.R0 %>% -->
<!--   select(system_ID, system_label, Temperature, sigmaH, KH, median) %>% -->
<!--   rename(R0 = median) %>%  -->
<!--   # Consider only 3 values of KH (on a log10-scale) -->
<!--   filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1 -->
<!--   # Choose a limited range of sigmaH values -->
<!--   filter(sigmaH > 10^0.5) %>% -->
<!--   # Group by plotting variables -->
<!--   group_by(system_ID, KH, sigmaH) %>% -->
<!--   # Calculate Topt (which.max requires grouping) -->
<!--   mutate(Topt = `Temperature`[which.max(R0)]) %>% -->
<!--   as_tibble() %>% -->
<!--   arrange(system_ID, sigmaH, Temperature) -->

<!-- ## Add a "point at infinity" for sigmaH -->
<!-- # Value of sigmaH to replace 'Inf' with for plotting -->
<!-- infinite_skew <- 10^3 + 2500 -->

<!-- # Get the largest value of log10(sigmaH) -->
<!-- max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>% -->
<!--   select(sigmaH) %>% -->
<!--   max() %>% -->
<!--   log10() -->

<!-- # Used to create a gap dividing finite and infinite sigmaH -->
<!-- infinite_divide <- 10^mean(c(3, log10(infinite_skew))) -->

<!-- # add a second proxy sigmaH point at infinity to make the values easier to see there -->
<!-- temp <- filter(R0_df, is.infinite(sigmaH)) %>% -->
<!--   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide)) -->
<!-- # Create a proxy sigmaH variable that replaces Inf with infinite_skew -->
<!-- R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH), -->
<!--                                              sigmaH, infinite_skew -->
<!-- )) -->
<!-- R0_df <- add_row(R0_df, temp) %>% distinct() -->

<!-- ## Compute mosquito thermal tolerance range (minimum and maximum) -->
<!-- temp_MosqThermRange_df <- MosqThermRange_df %>% -->
<!--   select(system_label, CTmin_V0, CTmax_V0) -->

<!-- ## PLOTTING ## -->

<!-- ## Options -->
<!-- # Define sigmaH tick breaks and labels -->
<!-- sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew) -->
<!-- sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$")) -->

<!-- # Labels for facet rows -->
<!-- R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10)) -->
<!-- mylabels <- as_labeller(c( -->
<!--   `0.1` = "0.1 vertebrate hosts / ha", -->
<!--   `1` = "1 vertebrate host / ha", -->
<!--   `10` = "10 vertebrate hosts / ha" -->
<!-- )) -->

<!-- # Breaks used to decide fill for the heat map -->
<!-- fill_breaks <- c(1, seq(5, 20, by = 5), Inf) -->

<!-- # Define colors for heat map so that values of R0>1 go from yellow to red -->
<!-- my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd")))) -->

<!-- ## PLOT ## -->
<!-- R0_plot <- R0_df %>% -->
<!--   ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) + -->

<!--   # Mosquito thermal tolerance range lines -->
<!--   geom_hline( -->
<!--     data = temp_MosqThermRange_df, -->
<!--     aes(yintercept = CTmin_V0, colour = "VTTR"), -->
<!--     lwd = 1.275 -->
<!--   ) + -->
<!--   geom_hline( -->
<!--     data = temp_MosqThermRange_df, -->
<!--     aes(yintercept = CTmax_V0, colour = "VTTR"), -->
<!--     lwd = 1.275 -->
<!--   ) + -->

<!--   # R0 contours for FINITE sigmaH: -->
<!--   geom_contour_filled( -->
<!--     data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98), -->
<!--     breaks = fill_breaks -->
<!--   ) + -->

<!--   # R0 contours for INFINITE sigmaH: -->
<!--   geom_contour_filled( -->
<!--     data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02), -->
<!--     breaks = fill_breaks -->
<!--   ) + -->

<!--   # R0 = 1 contour: -->
<!--   geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) + -->

<!--   # Topt curve: -->
<!--   geom_line( -->
<!--     # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one -->
<!--     mapping = aes( -->
<!--       x = sigmaH_proxy, -->
<!--       y = Topt, -->
<!--       colour = "Topt" -->
<!--     ), -->
<!--     lwd = 1, -->
<!--     linetype = 1 -->
<!--   ) + -->

<!--   # white lines breaking up finite/infinite sigmaH values -->
<!--   geom_vline( -->
<!--     aes(xintercept = 0.85 * infinite_divide), -->
<!--     colour = "white", -->
<!--     lwd = .8, -->
<!--     show.legend = FALSE -->
<!--   ) + -->
<!--   geom_vline( -->
<!--     aes(xintercept = infinite_divide), -->
<!--     colour = "white", -->
<!--     lwd = .8, -->
<!--     show.legend = FALSE -->
<!--   ) + -->
<!--   geom_vline( -->
<!--     aes(xintercept = 1.2 * infinite_divide), -->
<!--     colour = "white", -->
<!--     lwd = .8, -->
<!--     show.legend = FALSE -->
<!--   ) + -->

<!--   # x-axis: -->
<!--   scale_x_log10( -->
<!--     name = TeX("Vertebrate host biting tolerance (bites per host per day)"), -->
<!--     breaks = sigmaH_breaks, -->
<!--     labels = sigmaH_labels, -->
<!--     expand = c(0, 0) -->
<!--   ) + -->

<!--   # y-axis: -->
<!--   scale_y_continuous( -->
<!--     name = expression("Temperature "(degree * C)), -->
<!--     expand = c(0, 0), -->
<!--     limits = c(14, 36), -->
<!--     breaks = seq(10, 36, by = 2) -->
<!--   ) + -->

<!--   # color: -->
<!--   scale_colour_manual( -->
<!--     name = "", -->
<!--     labels = c( -->
<!--       "R0=1" = unname(TeX("$R_0=1$")), -->
<!--       "Topt" = "Transmission\nthermal\noptimum", -->
<!--       "VTTR" = "Mosquito\nthermal\ntolerance\nlimit" -->
<!--     ), -->
<!--     values = c("black", "purple", "grey"), -->
<!--     guide = guide_legend( -->
<!--       order = 1, -->
<!--       keyheight = unit(2, "cm"), -->
<!--       override.aes = list(size = 6) -->
<!--     ) -->
<!--   ) + -->

<!--   # fill: -->
<!--   scale_fill_manual( -->
<!--     name = TeX("$R_0$"), -->
<!--     values = my.cols, -->
<!--     guide = guide_colorsteps( -->
<!--       order = 2, -->
<!--       breaks = fill_breaks, -->
<!--       barheight = unit(8, "cm") -->
<!--     ) -->
<!--   ) + -->

<!--   # faceting: -->
<!--   facet_rep_grid( -->
<!--     rows = vars(system_label), -->
<!--     cols = vars(KH), -->
<!--     scales = "free_y", -->
<!--     labeller = labeller(.cols = mylabels), -->
<!--     repeat.tick.labels = "left" -->
<!--   ) + -->

<!--   # theme options: -->
<!--   theme_minimal_hgrid(11) + -->
<!--   theme( -->
<!--     axis.line = element_line(), -->
<!--     panel.spacing = unit(1, "lines"), -->
<!--     legend.text = element_text(size = 11), -->
<!--     legend.text.align = 0, -->
<!--     strip.text = ggtext::element_markdown( -->
<!--       size = 8, -->
<!--       hjust = 0 -->
<!--     ) -->
<!--   ) -->

<!-- # Plot it -->
<!-- R0_plot -->
<!-- ``` -->

<!-- ```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'} -->
<!-- Topt_df <- data.Topt %>%  -->
<!--   pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
<!--               names_from = variable, -->
<!--               values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%  -->
<!--   right_join(read_rds("results/CT_vals.rds") %>%  -->
<!--                filter(variable == "CTwidth") %>%  -->
<!--                pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"),  -->
<!--                            names_from = "variable", -->
<!--                            values_from = c("mean", "median", "lowHCI", "highHCI"))) %>%  -->
<!--   filter(sigmaH %in% c(1, 10, 100, Inf)) %>%  -->
<!--   # filter(mean_CTwidth>0) %>%  -->
<!--   select(-c(mean_CTwidth, median_CTwidth, lowHCI_CTwidth, highHCI_CTwidth)) %>% -->
<!--   rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,  -->
<!--          highHCI = highHCI_Topt) %>%  -->
<!--   # filter(KH > 0.01) %>% -->
<!--   # filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>% -->
<!--   group_by(KH) %>% -->
<!--   # Arrange along the plotting variables -->
<!--   arrange(system_ID, KH, mean) %>% -->
<!--   arrange(sigmaH) %>% -->
<!--   ungroup() -->

>>>>

data.R0_norm <- data.R0 %>%
  filter(KH %in% newKH_vals) %>%
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize variables to have a maximum of 1
  group_by(system_ID, Model, sigmaH, KH) %>%
  # mutate(mean_norm = mean / max(mean)) %>%
  mutate(median_norm = median / max(median)) %>%
  # mutate(highHCI_norm = highHCI / max(median)) %>%
  # mutate(lowHCI_norm = lowHCI / max(median)) %>%
  arrange(system_ID, sigmaH, KH, Temperature, median_norm)

@@

Toptalt_df <- data.Topt %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, median) %>%
  mutate(sigmaH_proxy = sigmaH)

@@

# Plot median of Topt heat map
Toptalt_plots <- Toptalt_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # Topt for FINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy < 10^2.2),
    breaks = Topt_breaks
  ) +
  # Topt for INFINITE sigmaH:
  # take median of median to hide variation from artifacts of uncertainty
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy > infinite_skew) %>%
      group_by(system_ID) %>%
      mutate(median = median(median), .groups = "keep"),
    size = 1,
    breaks = Topt_breaks
  ) +
  # # R0 = 1 contour: cheat and use where CTwidth = 0 (i.e. where R0<1 at any temperature)
  geom_contour(
    data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
    aes(y = sigmaH, z = median, colour = "R0 = 1"),
    breaks = min(filter(data.CT, variable == "CTwidth", median > 0)$median),
    size = 1
  ) +
  # geom_contour(data = data.R0_norm,
  #              aes(y = sigmaH, z = median, colour = "R0=1"), breaks = c(1), size = 1) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

@@

CTwidth_df <- data.CT %>%
  filter(variable == "CTwidth") %>%
  # filter(sigmaH < 10^2.2) %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>%
  ungroup()

@@

CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < 10^2.2)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(
    CTwidth_df,
    sigmaH_proxy > 10^2.4,
    sigmaH_proxy < infinite_divide
  )) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Parasite thermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

# Supplementary Figures

```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} R0 heatmap expressing threshold (R0 = 1) as a contour and thermal optimum as ridges.'}
# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.

# !!! [] get enough values of R0 across sigmaH and KH to do a heatmap (21 each?)

# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
# y = Temperature
# color = R0
# curves:
#   R0 = 1 contour (black curve)
#   Topt (red curve)

# Facets:
# Rows = levels of vertebrate host population density
# Columns = two MBPT systems
# Total = 6 plots

## Set up plot data frame
# We re-create the output data frame so that we can vary sigmaH correctly.
# We also drop the resolution of KH down to just three values
# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"

## Configure data frame for plotting
R0_df <- data.R0 %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
  rename(R0 = median) %>%
  # Consider only 3 values of KH (on a log10-scale)
  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
  # Choose a limited range of sigmaH values
  filter(sigmaH > 10^0.5) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)

## Add a "point at infinity" for sigmaH
# Value of sigmaH to replace 'Inf' with for plotting
infinite_skew <- 10^3 + 2500

# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^mean(c(3, log10(infinite_skew)))

R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 3)

# Get the largest value of log10(sigmaH)
max_log10sigmaH <- filter(R0_df, is.finite(sigmaH)) %>%
  select(sigmaH) %>%
  max() %>%
  log10()

# # add a second proxy sigmaH point at infinity to make the values easier to see there
# temp <- filter(R0_df, is.infinite(sigmaH)) %>%
#   mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH, 1.2 * infinite_divide))
# # Create a proxy sigmaH variable that replaces Inf with infinite_skew
# R0_df <- mutate(R0_df, sigmaH_proxy = ifelse(is.finite(sigmaH),
#                                              sigmaH, infinite_skew
# ))
# R0_df <- add_row(R0_df, temp) %>% distinct()

## Compute mosquito thermal tolerance range (minimum and maximum)
temp_MosqThermRange_df <- MosqThermRange_df %>%
  select(system_label, CTmin_V0, CTmax_V0)

## PLOTTING ##

## Options
# Define sigmaH tick breaks and labels
sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), infinite_divide, infinite_skew)
sigmaH_labels <- c(paste(c(10^c(seq(-1, 3, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

# Labels for facet rows
R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
mylabels <- as_labeller(c(
  `0.1` = "0.1 vertebrate hosts / ha",
  `1` = "1 vertebrate host / ha",
  `10` = "10 vertebrate hosts / ha"
))

# Breaks used to decide fill for the heat map
fill_breaks <- c(1, seq(5, 20, by = 5), Inf)

# Define colors for heat map so that values of R0>1 go from yellow to red
my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature, z = R0)) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = temp_MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = temp_MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    breaks = fill_breaks
  ) +
  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    breaks = fill_breaks
  ) +
  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1"), breaks = c(1), size = 1) +
  # Topt curve:
  geom_line(
    # data = filter(R0_df, R0>1), # uncomment to only display Topt when R0 exceeds one
    mapping = aes(
      x = sigmaH_proxy,
      y = Topt,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +
  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels,
    expand = c(0, 0)
  ) +
  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(14, 36),
    breaks = seq(10, 36, by = 2)
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\nthermal\ntolerance\nlimit"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +
  # faceting:
  facet_rep_grid(
    rows = vars(system_label),
    cols = vars(KH),
    scales = "free_y",
    labeller = labeller(.cols = mylabels),
    repeat.tick.labels = "left"
  ) +
  # theme options:
  theme_minimal_hgrid(11) +
  theme(
    axis.line = element_line(),
    panel.spacing = unit(1, "lines"),
    legend.text = element_text(size = 11),
    legend.text.align = 0,
    strip.text = ggtext::element_markdown(
      size = 8,
      hjust = 0
    )
  )

# Plot it
R0_plot
```

```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
Topt_df <- data.Topt %>%
  pivot_wider(id_cols = c("system_label", "Model", "sigmaH", "KH"),
              names_from = variable,
              values_from = c("mean", "median", "lowHCI", "highHCI"))  %>%
  rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
         highHCI = highHCI_Topt) %>%
  # Arrange along the plotting variables
  arrange(system_label, KH, median, sigmaH) %>%
  ungroup()

# PLOTTING
Topt_plot <- Topt_df %>%
  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
  ## Set up plot ##
  # color = sigmaH
  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
  # Topt curves:
  geom_path(aes(y = median), lwd = 1) +
  # x-axis: log10 scale, no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.01, 2E4),
    breaks = 10^seq(-2, 4),
    labels = TeX(c(
      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
    ))
  ) +
  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0,0), # c(0.05, 0.05),
    limits = c(21,30.5), # mean: 21-31, median: 21-32
    breaks = seq(21,32, by = 1)
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  scale_fill_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  # faceting:
  facet_wrap(~system_label, nrow = 2, labeller = labeller()) +
  # theme options:
  theme_minimal(16) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Topt_plot)
```

```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=8, fig.align='center', fig.cap='\\label{fig:Topt_plots} Transmission thermal optimum as a function of vertebrate host availability.'}

# x-axis = vertebrate host biting tolerance
# y-axis = thermal optimum
# color = vertebrate host population density

infinite_skew <- 4500 # 10000

Topt_df <- Topt_df %>% 
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
                               sigmaH,
                               infinite_skew))
Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)
